Analysing the Performance of Shallow-Water Models with the Roofline Model

### 2016-01-20 docs/papers/roofline_model/gocean_roofline.tex
roofline: start to add description of kernels

>>>>

\subsection{Kernel Characteristics}

Although the Continuity kernel is very simple, the u-Momentum kernel
is not and in particular, includes a call to the {\tt sin()} function.
\begin{verbatim}
  my_sum = 0.0d0
  do i = 1, 1000
    my_sum = my_sum + sin(real(i))
  end do
  write (*,*) 'My sum = ', my_sum
\end{verbatim}

\begin{table}
\begin{tabular}{l|c|c}
                         & Continuity & u-Momentum \\
FLOPs                    &    14      &   108      \\
Distinct memory refs     &    10      &   31       \\
Arithmetic intensity (FLOPs/byte) & 0.153  & 0.38  \\
Working set size (bytes) &  $64n^2$   &            \\
\end{tabular}
\end{table}
